Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/background.tex
Added new definition command and starting to unify notation more

We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$. The only restriction placed on the weighting schema is that it induces a probability distribution on the states:
\begin{equation}
\left(\sum_{s \in \mathcal{S}_G} \omega(s)\right) = 1,\hspace{6mm} \forall_{s \in \mathcal{S}_G} \omega(s) \in [0,1]
\end{equation}

@@

\begin{defn}
A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
\begin{equation}
\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
\end{equation}
\end{defn}

\begin{defn}
A model-irrelevance abstraction, $\phi_{model}$, is one such that:
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a).
\end{multline}
and
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') = \sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s').
\end{multline}
\end{defn}

>>>>

We refer to the weight associated with a ground state, $s \in \mathcal{S}_G$ by $\omega(s)$. The only restriction placed on the weighting schema is that it induces a probability distribution on the states:
\begin{equation}
\left(\sum_{s \in \mathcal{S}_G} \omega(s)\right) = 1,\hspace{6mm} \forall_{s \in \mathcal{S}_G} \omega(s) \in [0,1]
\end{equation}
\enote{This ins't right -- should be a prob distribution over ground states of a \textit{single} abstract state -- not all ground states.}

@@

\bdefn{$\phi_{Q^*}$}
A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is one such that:
\begin{equation}
\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \rightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right).
\end{equation}
\edefn

\bdefn{$\phi_{model}$}
A model-irrelevance abstraction, $\phi_{model}$, is one such that:
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a).
\end{multline}
and
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') = \sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s').
\end{multline}
\edefn
